Preprocess

### 2024-02-12 src/preprocess.Rmd
Replace ChatGPT with GPT for accurate reference

    model_chatgpt3 = bind_rows(

@@

            "../tmp/healsl_rd1_rapid_chatgpt3_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_chatgpt3_v1.csv",

@@

    ) %>% rename(chatgpt3_icd10 = api_chat_icd),
    model_chatgpt4 = bind_rows(

@@

            "../tmp/healsl_rd1_rapid_chatgpt4_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_chatgpt4_v1.csv",

@@

    ) %>% rename(chatgpt4_icd10 = api_chat_icd),

@@

# Get chatgpt3 coded records
out_cgpt3 <- out_coded %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)
out_cgpt3_agree <- out_coded_agree %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)
out_cgpt3_cghr10 <- out_coded_cghr10 %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)
out_cgpt3_cghr10_agree <- out_coded_cghr10_agree %>% filter(
    !is.na(chatgpt3_icd10) & !is.null(chatgpt3_icd10)
)

# Get chatgpt3 coded records converted to cghr10
out_cgpt3_xcghr10 <- out_cgpt3 %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)
out_cgpt3_xcghr10_agree <- out_cgpt3_agree %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)
out_cgpt3_xcghr10_cghr10 <- out_cgpt3_cghr10 %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)
out_cgpt3_xcghr10_cghr10_agree <- out_cgpt3_cghr10_agree %>% filter(
    !is.na(chatgpt3_cghr10) & !is.null(chatgpt3_cghr10)
)

@@

# Get chatgpt4 coded records
out_cgpt4 <- out_coded %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)
out_cgpt4_agree <- out_coded_agree %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)
out_cgpt4_cghr10 <- out_coded_cghr10 %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)
out_cgpt4_cghr10_agree <- out_coded_cghr10_agree %>% filter(
    !is.na(chatgpt4_icd10) & !is.null(chatgpt4_icd10)
)

# Get chatgpt4 coded records converted to cghr10
out_cgpt4_xcghr10 <- out_cgpt4 %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)
out_cgpt4_xcghr10_agree <- out_cgpt4_agree %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)
out_cgpt4_xcghr10_cghr10 <- out_cgpt4_cghr10 %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)
out_cgpt4_xcghr10_cghr10_agree <- out_cgpt4_cghr10_agree %>% filter(
    !is.na(chatgpt4_cghr10) & !is.null(chatgpt4_cghr10)
)

@@

# Get interva5 coded records in wva2016
out_iva5 <- out_who %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_agree <- out_who_agree %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_cghr10 <- out_who_cghr10 %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_chr10_agree <- out_who_cghr10_agree %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)

@@

# Get insilicova coded records in wva2016
out_isva <- out_who %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_agree <- out_who_agree %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_cghr10 <- out_who_cghr10 %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_chr10_agree <- out_who_cghr10_agree %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)

>>>>

    model_gpt3 = bind_rows(

@@

            "../tmp/healsl_rd1_rapid_gpt3_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_gpt3_v1.csv",

@@

    ) %>% rename(gpt3_icd10 = api_chat_icd),
    model_gpt4 = bind_rows(

@@

            "../tmp/healsl_rd1_rapid_gpt4_v1.csv",

@@

            "../tmp/healsl_rd2_rapid_gpt4_v1.csv",

@@

    ) %>% rename(gpt4_icd10 = api_chat_icd),

@@

# Get gpt3 coded records
out_cgpt3 <- out_coded %>% filter(
    !is.na(gpt3_icd10) & !is.null(gpt3_icd10)
)
out_cgpt3_agree <- out_coded_agree %>% filter(
    !is.na(gpt3_icd10) & !is.null(gpt3_icd10)
)
out_cgpt3_cghr10 <- out_coded_cghr10 %>% filter(
    !is.na(gpt3_icd10) & !is.null(gpt3_icd10)
)
out_cgpt3_cghr10_agree <- out_coded_cghr10_agree %>% filter(
    !is.na(gpt3_icd10) & !is.null(gpt3_icd10)
)

# Get gpt3 coded records converted to cghr10
out_cgpt3_xcghr10 <- out_cgpt3 %>% filter(
    !is.na(gpt3_cghr10) & !is.null(gpt3_cghr10)
)
out_cgpt3_xcghr10_agree <- out_cgpt3_agree %>% filter(
    !is.na(gpt3_cghr10) & !is.null(gpt3_cghr10)
)
out_cgpt3_xcghr10_cghr10 <- out_cgpt3_cghr10 %>% filter(
    !is.na(gpt3_cghr10) & !is.null(gpt3_cghr10)
)
out_cgpt3_xcghr10_cghr10_agree <- out_cgpt3_cghr10_agree %>% filter(
    !is.na(gpt3_cghr10) & !is.null(gpt3_cghr10)
)

@@

# Get gpt4 coded records
out_cgpt4 <- out_coded %>% filter(
    !is.na(gpt4_icd10) & !is.null(gpt4_icd10)
)
out_cgpt4_agree <- out_coded_agree %>% filter(
    !is.na(gpt4_icd10) & !is.null(gpt4_icd10)
)
out_cgpt4_cghr10 <- out_coded_cghr10 %>% filter(
    !is.na(gpt4_icd10) & !is.null(gpt4_icd10)
)
out_cgpt4_cghr10_agree <- out_coded_cghr10_agree %>% filter(
    !is.na(gpt4_icd10) & !is.null(gpt4_icd10)
)

# Get gpt4 coded records converted to cghr10
out_cgpt4_xcghr10 <- out_cgpt4 %>% filter(
    !is.na(gpt4_cghr10) & !is.null(gpt4_cghr10)
)
out_cgpt4_xcghr10_agree <- out_cgpt4_agree %>% filter(
    !is.na(gpt4_cghr10) & !is.null(gpt4_cghr10)
)
out_cgpt4_xcghr10_cghr10 <- out_cgpt4_cghr10 %>% filter(
    !is.na(gpt4_cghr10) & !is.null(gpt4_cghr10)
)
out_cgpt4_xcghr10_cghr10_agree <- out_cgpt4_cghr10_agree %>% filter(
    !is.na(gpt4_cghr10) & !is.null(gpt4_cghr10)
)

@@

# Get interva5 coded records in wva2016
out_iva5 <- out_who %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_agree <- out_who_agree %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_cghr10 <- out_who_cghr10 %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)
out_iva5_cghr10_agree <- out_who_cghr10_agree %>% filter(
    !is.na(interva5_wva2016) & !is.null(interva5_wva2016)
)

@@

# Get insilicova coded records in wva2016
out_isva <- out_who %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_agree <- out_who_agree %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_cghr10 <- out_who_cghr10 %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
out_isva_cghr10_agree <- out_who_cghr10_agree %>% filter(
    !is.na(insilicova_wva2016) & !is.null(insilicova_wva2016)
)
